\documentclass[9pt]{extarticle}
\usepackage{set space}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{engtlc}
\usepackage{mathrsfs}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{float}
\usepackage{multicol}
\geometry{margin=.75in}
\setlength{\parindent}{0pt}
\setlength{\headheight}{0pt}
\pagenumbering{gobble}
\usepackage{titlesec}

\title{Resume}
\author{Ed Yother}


\begin{document}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{\hrule}

\begin{huge}
\begin{center}
    \textbf{Edgar Yother}
\end{center}

(636)344-0890 \hfill 201 Cumberland Avenue 

ed@edyother.com \hfill West Lafayette, Indiana 47906 
\end{huge}

\section*{Skills}

\begin{multicols}{3}
\subsection*{Technical}
\begin{itemize}
    \item Field Measuring  
    \item 2D Drafting
    \item 3D Modeling
    \item Creating As-Built Floor Plans
    \item Designing Miscellaneous and \\
        Ornamental Metals 
    \item Creating Shop Drawings
    \item Metal Fabrication  
    \item Welding  
\end{itemize}
\columnbreak
\subsection*{Software}
\begin{itemize}
    \item Revit
    \item AutoCAD  
    \item SolidWorks  
    \item OnShape
    \item Fusion 360
    \item BendTech  
\end{itemize}
\columnbreak
\subsection*{Languages}
\begin{itemize}
    \item AutoLISP
    \item AutoHotkey
    \item BASH
    \item PowerShell
    \item HTML
    \item \LaTeX
\end{itemize}
\end{multicols}

\section*{Employment} 

\textbf{KJG Architecture and Engineering} \hfill September 2016 to Present

\textit{CAD Technician} \hfill West Lafayette, Indiana

\begin{itemize}
    \item Take measurements of buildings and draw existing floor plans. 
    \item Any drafting that is needed by the architects and engineers in the office.
    \item Photography for the company website.
    \end{itemize}

\textbf{BenFab Architectural Metalworks} \hfill November 2014 to September 2016

\textit{Fabrication Design Manager} \hfill Folcroft, Pennsylvania

\begin{itemize}
    \item Design, coordination, and purchasing materials for the development of ornamental metals and structural steel including: 
        \begin{multicols}{3}
        \begin{itemize}
            \item Field measuring
            \item Creating shop drawings 
            \item Develop bills of materials 
            \item Order material  
            \item Coordinate with architect or construction project manager
            \end{itemize}
        \end{multicols}
    \item Establish standard company drawing practices.
    \item Training other drafters in advanced skills in field measuring, and drafting. 
    \item Responsible for the review of the International Building Code (IBC) and the Americans with Disabilities Act (ADA) to ensure compliance.
\end{itemize}

\hfill

\textbf{Cohen Metals} \hfill May 2013 to November 2014

\textit{Technical Lead/Welder/Fabricator/Drafter} \hfill Broomall, Pennsylvania/Philadelphia, Pennsylvania 

\begin{itemize}
    \item Assigned tasks and supervised a team of welders and fabricators.
    \item Design and fabrication of miscellaneous and ornamental metals as well as structural steel.
\end{itemize}

\textbf{The Folk School of St Louis} \hfill March 2011 to June 2012

\textit{Instructor} \hfill Maplewood, Missouri

\begin{itemize}
    \item Teaching mandolin, tenor banjo, and Irish set dancing.
\end{itemize}

\textbf{Homemaker/Stay at Home Parent} \hfill March 2009 to May 2013

\textit{Primary caregiver for two young children} \hfill Hebron, Connecticut/Saint Charles, Missouri/Aston, Pennsylvania

\newpage
\textbf{Quality Welding} \hfill July 2005 to March 2009

\textit{Welder/Fabricator/Installer/Drafter} \hfill Bristol, Connecticut

\begin{itemize}
    \item Performed all tasks involved in the fabrication of miscellaneous and ornamental metals including: 
        \begin{multicols}{3}
\begin{itemize}
    \item Field measuring 
    \item Design 
    \item Creation of shop drawings 
    \item Estimating material cost 
    \item Fabrication 
    \item Welding 
    \item Grinding 
    \item Sandblasting 
    \item Painting 
    \item Installation
\end{itemize}
\end{multicols}
\end{itemize}

\textbf{Highland Park Market} \hfill September 2004 to July 2005

\textit{Deli Clerk} \hfill Glastonbury, Connecticut

\begin{multicols}{2}
\begin{itemize}
    \item Filled requests for customers.
    \item Opening and closing of the deli department.
\end{itemize}
\end{multicols}

\textbf{Millwrights Union, Local \#1121} \hfill July 2004 to January 2005 

\textit{Apprentice} \hfill Allston, Massachusetts

\hfill

\textbf{Howmet Castings} \hfill May 2004 to July 2004 

\textit{Welder} \hfill Winsted, Connecticut

\begin{itemize}
    \item TIG hard facing of blades for turbine engines.
\end{itemize}

\textbf{Northrop Grumman Ship Systems} \hfill August 2003 to May 2004 

\textit{Welder} \hfill Avondale, Louisiana

\begin{itemize}
    \item Welding and grinding of structural parts for military and commercial ships.
\end{itemize}

\section*{Education and Training}
\textbf{Paier College of Art}  \hfill September 1996 to December 1998

Hamden, Connecticut \hfill Diploma of Fine Arts 

\hfill \textbf{Major: Photography}

\hfill

\textbf{Delgado Community College} \hfill March 2003 to May 2003

New Orleans, Louisiana

\begin{itemize}
    \item Welding
\end{itemize}

\textbf{Manchester Community College} \hfill January 2007 to December 2009

Manchester, Connecticut

\begin{multicols}{3}
\begin{itemize}
    \item 2D Drafting
    \item 3D Modeling
\end{itemize}
\end{multicols}

\textbf{St Charles Community College} \hfill August 2010 to June 2012

St Charles, Missouri

\begin{multicols}{3}
\begin{itemize}
    \item Architectural Drafting
    \item Civil Drafting
    \item Piping Drafting
    \item Algebra
    \item Office Applications
\end{itemize}
\end{multicols}

\textbf{Ivy Tech} \hfill January 2022 to Present

Lafayette, Indiana

\begin{multicols}{3}
\begin{itemize}
    \item Algebra
    \item Mechanical Design
    \item Circuit Analysis
\end{itemize}
\end{multicols}

\end{document}
